Effects of the body force on the evacuation dynamics

### 2019-12-29 paper.tex
Add files via upload
Update de Guillermo Frank.

@@

\subfloat[(a)]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}
\label{venn_2parameters}}\

\subfloat[(b)]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
\label{venn_3parameters}}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix_1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$ (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

@@

\subsection{\label{reduced-in-units} Reduced-in-units equation of motion}

@@

\section{appendix_1}

@@

\begin{equation}
 \displaystyle\frac{d\mathbf{v}'}{dt'}=
 \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
 \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
 \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
\end{equation}

>>>>

\author[add1]{I.M.~Sticco}
 \address[add1]{Departamento de F\'\i sica, Facultad de Ciencias 
Exactas y Naturales, Universidad de Buenos Aires,\\
 Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
 %Lines break automatically or can be forced with \\
 \author[add2]{G.A.~Frank}
 \address[add2]{Unidad de Investigaci\'on y Desarrollo de las 
Ingenier\'\i as, Universidad Tecnol\'ogica Nacional, Facultad Regional Buenos 
Aires, Av. Medrano 951, 1179 Buenos Aires, Argentina.}
 %Lines break automatically or can be forced with \\
\author[add1,add3]{C.O.~Dorso\corref{cor1}}%
 \cortext[cor1]{codorso@df.uba.ar}
%\affiliation{Departamento de F\'\i sica, Facultad de Ciencias Exactas y 
%Naturales, Universidad de Buenos Aires,\\
% Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}%
% \altaffiliation[Also at ]{Instituto de F\'\i sica de Buenos Aires, Pabell\'on 
%I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
\address[add3]{Instituto de F\'\i sica de Buenos Aires,
Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
 %\affiliation{Departamento de F\'\i sica, Facultad de Ciencias 
%Exactas y Naturales, Universidad de Buenos Aires,\\
% Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}

@@

\subfloat[\label{venn_2parameters}]
{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}}
\hfill    
\subfloat[\label{venn_3parameters}]
{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix_1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

@@

@@

\section{\label{appendix_1} Reduced-in-units equation of motion}

@@

\begin{equation}
 \displaystyle\frac{d\mathbf{v}'}{dt'}=
 \hat{\mathbf{e}}_d-\mathbf{v}'+\mathcal{A}\,e^{R'-r'}\,
 \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
 \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathcal{K}_c\,\hat{\mathbf{n}}\bigg]
\end{equation}
